Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-29 paper/ms.tex
Update numbers

To allow for potential small inaccuracies in the fiducial coordinate systems,
we also subtract the best fit $\text{A} \sin{\left(\phi + \text{B}\right)} +
\text{C}$ curve from the midplane as a function of azimuth. For $\text{A}$,
the values are $-165$, $45$, $9\,\pc$ and for $\text{C}$ the values are $-69$,
$19$, and $-18\,\pc$ for m12i, m12f, and m12m, respectively \Gus{Double check
numbers}. For the assumed solar radius of $8.2\,\kpc$, we can approximate the
angle offset for the $z$-axis from the values of $\text{A}$ --- we compute
\Gus{$1.15$, $0.31$, and $0.06\,\deg$} for m12i, m12f, and m12m. These angle
offsets are consistent with the values given in \citet{2018arXiv180610564S}
for the difference between the $z$-axis as defined by the gas and stars.

>>>>

To allow for potential small inaccuracies in the fiducial coordinate systems,
we also subtract the best fit $\text{A} \sin{\left(\phi + \text{B}\right)} +
\text{C}$ curve from the midplane as a function of azimuth. For $\text{A}$ the
values are $-174$, $62$, and $3.8\,\pc$, for $\text{B}$ the values are $0.3$,
$0.65$, and $0.021\,\text{rad}$ and for $\text{C}$ the values are $-47$, $18$,
and $-15\,\pc$ for m12i, m12f, and m12m, respectively. For the assumed solar
radius of $8.2\,\kpc$, we can approximate the angle offset for the $z$-axis
from the values of $\text{A}$ --- we compute $1.22$, $0.43$, and $0.03\,\deg$
for m12i, m12f, and m12m. These angle offsets are consistent with the values
given in \citet{2018arXiv180610564S} for the difference between the $z$-axis
as defined by the gas and stars.
